Model-based variable selection for regression with highly correlated variables.

### 2014-04-18 www/article13.tex
up title
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@546 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{Model-based variable selection for regression with highly correlated variables.}

@@

\begin{document}
\begin{center}
{\Large
	{\sc Model-based pretreatment for regression \\ with highly correlated variables.}
}
\bigskip

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
%\title{Model-based variable selection for regression with highly correlated variables.}

@@

\begin{document}
\begin{center}
{\Large
	{\sc Model-based variable selection for regression \\ with highly correlated variables.}
}
\bigskip
